Huffing, puffing, wheezing. These stairs will not be the end of me. I am a strong woman and I will not let a few flights of stairs stop me. The sweat drips down my thighs, the warm blood pumps through my veins. I struggle. I gasp. Grasping at the handrail, I carry on.

Four hundred pounds isn't even that much. I'm not even the fattest person I know. Aunt Susan is at least a hundred pounds heavier than me, or so she says. She's at least a hundred fifty heavier and growing. But not me, I will lose this weight, I will survive this disease. So I continue, step after step, stair after stair, flight after flight. All three of them.

After the first flight, I take a break. Sitting on a step is too difficult and the janitor got mad at me last time. Apparently blocking people's paths is worse than losing weight. It's not my fault I'm this way, it's just how I am. Nothing but hard work can change that. I am dedicated to changing who I am, have been for three years now.

Breath caught, I persevere through the next flight of stairs. ``You've got this,'' I tell myself every step of the way. After the second flight of stairs, though, it's not enough encouragement. So I pull out the big gun~--- the surprise on my desk. All the motivation I ever need to better myself, to lose weight, to be the ideal, is daily waiting for me every day on my desk.

The air gets thinner the farther I go. I struggle for breath, I pant, I rest and recuperate. I carry on. It's been three hard years. The hardest part has been seeing the needle on my scale refuse to budge. I work, I sweat, I cry, but the needle doesn't drop. Yet I know that with my continued efforts I will eventually reach my goal. I will lose weight.

The end is in sight, it will be mine. I reach the final step in record time, pat myself on the back, and proceed to my office. Here it is, the motivation to keep me working every day to better myself. I plump down into my oversized chair, body weary from the exertions of the day, and proceed to eat an entire bucket of fried chicken.
