\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}

\usepackage{fontspec}
\setmainfont[BoldFont={HoeflerText-Bold},ItalicFont={Hoefler Text Italic},BoldItalicFont={Hoefler Text Black Italic},SmallCapsFont={HoeflerText-RomanSC},Ligatures={NoCommon, TeX}]{Hoefler Text}
\setmonofont[Ligatures={TeX}]{Source Code Pro Medium}

\usepackage[normalem]{ulem}

\title{Dating and Marrying Your Own Sister}
\author{Colby Goettel}

\begin{document}
\maketitle

% 1) Audience Analysis
% Write one or two brief paragraphs analyzing your target audience and their values, beliefs, and assumptions. You are writing your paper for a general American audience: imagine that your argument will be distributed in a national newspaper or magazine. Within this general audience, you will need to identify who constitutes your specific audience. Who might find your claim initially unacceptable? What kinds of groups or individuals would care about your issue (e.g., educators, health care providers, government officials, parents, etc.)? What values, beliefs, or assumptions do they hold about your issue? Do you personally know any individuals who would disagree with your stance? What would their probable response to your argument be?

% target audience: lonely guys with available sisters
% audience values: marriage

% Marriage is a deep, longing desire in many men's lives.
% Family is forever.

Before reading, please keep in mind that this is dark satire.

The target audience is lonely guys with available sisters. Marriage is one of their deep, longing desires. They are typically shy and don't have many social connections. Maybe they do and they just have a really hot sister. They're already best friends. No more social anxiety having to meet her parents, either! Never have to deal with unruly in-laws or figure out where you're going to stay for the holidays. It's a win-win for everyone. This is the epitome of keeping it in the family; after all, families are forever.

This claim is initially unacceptable to prudes, but they'll come around. The stakeholders include parents, children, government policy makers. Parents care about their children being happy. They also want grandchildren.

% 2) Consequential Issue Question
% Write out the WATCO question (What are the consequences of A on B?) that your paper will answer.
What are the consequences of dating your own sister on your progression.

% 3) Pro/Con Analysis
% Summarize the arguments for and against your issue. You can write this pro/con analysis in the form of a bulleted list or as a paragraph.
Pros: already know her parents, best friends, know all of her likes and dislikes, don't have to worry about where you're going for the holidays, never have to deal with in-laws.

Cons: incest (more like wincest).

% 4) Preliminary Enthymeme
% Draft a preliminary enthymeme for your paper. This should include your claim, reason, and your assumption. Please follow the format below for writing your enthymeme (be sure to mark the terms and underline the verbs as shown):
Dating and marrying your own sister (A) \uline{benefits} (v1) lonely guys (B) because dating your sister (A$^\prime$) \uline{removes} (v2) complications from the dating scene (C).

% Banning the advertising of junk food to children (A) decreases (v1) childhood obesity rates (B)
% b/c
% Banning the advertising of junk food to children (A) decreases (v2) calorie consumption from junk food among children (C).

\end{document}
