\documentclass{article}
\usepackage[margin=1in]{geometry}

\title{Final Portfolio and Reflection}
\author{Colby Goettel}

\begin{document}
\maketitle

% Tell me what grade you deserve on this assignment and why.
My final portfolio is worthy of a $630/700$ minimum, but more realistically a 650.

The following has been submitted in this portfolio, descriptions of each in-line, for a total of 14 pages:
\begin{itemize}
    \item Resume, 1 page. This is a strong resume. It got me an interview, where I got a great job offer. The job posting is attached. It is for a NOC (Network Operations Center) Support Engineer position with a data center in Orem. The resume is specifically tailored to a career in systems and network administration, two of the key responsibilities of a NOC engineer.
    \item Cover letter, 3 pages (if double spaced). This is a highly polished and well written cover letter that got me into graduate school (cover letter instructions attached). This cover letter went through ten revisions and was edited by multiple, outside sources with input from a couple more. I spent more time on this cover letter than any essay in this class. In fact, the first issue paper (which received an 85\%) was written in less than an hour and a half.
    \item NSA Snooping, 4 pages. This is a subject that I'm passionate about and it comes out in my writing. The revision gets to the argument quicker and more forcefully. I removed a lot of the riff raff that detracted from the point. I will also note that I opted to keep the essay more or less as is instead of adding more information about what the CIA and others have been doing. This helps keep the essay more in focus. The essay has enough background information, it doesn't need to completely overwhelm the audience with the atrocities committed by our government. Save that for another paper.
    \item Comcast merger, 5 pages. I shortened this essay, removing superfluous information, streamlining it. The conclusion better addresses the audience and does so concisely. The main reason this essay was marked down was because it wasn't long enough. That is no longer a problem in this context. It is a strong, persuasive essay that is deserving of top marks.
    \item Blog post, 1 page. This was a fun post to write about something I'm passionate about. It is well worded, conclusive, and easy to understand for non-Hebrew speakers.
\end{itemize}

All of these assignments got high marks, the average of which is around 630. With the revisions that have happened, the final portfolio is in the arena of a 650.

For a better idea of which revisions have happened, please navigate to the file in https://github.com/cgoettel/engl-312 and select \textit{History} from the upper right-hand menu. Then click on the icon on the right to see a diff between the current version and the selected version. This should work a lot better than trying to read the two side-by-side.

\end{document}
